AbxD01 Analysis

### 2015-02-25 abxD01_analysis.Rmd
Update to papers mkdwn pipeline

stackedbarcharts(file = "~/Documents/Github/abxD01/Figure 3/abxD01.final.tx2.subsample.alltitrations.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 3/alltitrations_tx2_barchart_ids.csv", divide = TRUE)

@@

@@

#what are the important variables (via permutation) #type 1 is mean decrease in accuracy, type 2 is mean decrease in node impurity
par(mfrow=c(1, 1)) 
varImpPlot(model_tx2, type=1)
#imp<-importance(model_tx2)
#most.imp<-rownames(imp[order(imp[, "%IncMSE"], decreasing=T)[1:17],])
```

@@

Input files found on github:
1. abxD01.final.tx.2.subsample.2.metro.relabund.D0s.csv

>>>>

stackedbarcharts(file = "~/Documents/Github/abxD01/Figure 3/abxD01.final.tx2.subsample.alltitrations.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 3/alltitrations_tx2_barchart_ids.csv", excludeGroup="untr", divide = TRUE)

@@

This figure shows the difference between the Day 0's in the delayed and original treatments for metronidazole.

@@

#what are the important variables (via permutation) #type 1 is mean decrease in accuracy, type 2 is mean decrease in node impurity
par(mfrow=c(1, 1)) 
varImpPlot(model_tx2, type=1)
#imp<-importance(model_tx2)
#most.imp<-rownames(imp[order(imp[, "%IncMSE"], decreasing=T)[1:17],])

@@

The file/fileIDS should be matched.
Input files on github folder Figure 5:
1. abxD01.final.tx.2.subsample.alldelay.forlogscale.csv
2. alldelay_tx2_barchart_ids.csv

stackedbarcharts(file = "~/Documents/Github/abxD01/Figure 5/abxD01.final.tx.2.subsample.alldelay.forlogscale.csv", fileIDS = "~/Documents/Github/abxD01/Figure 5/alldelay_tx2_barchart_ids.csv", divide = TRUE)
